\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-23 doc/USER_MANUAL/manual_SPECFEM3D.tex
changed www.paraview.com to www.paraview.org

OpenDX \url{http://www.opendx.org} is open-source based on IBM Data
Explorer, AVS \url{http://www.avs.com} is a trademark of Advanced
Visualization Systems, and ParaView \url{http://www.paraview.com}
is an open-source visualization platform.

>>>>

OpenDX \url{http://www.opendx.org} is open-source based on IBM Data
Explorer, AVS \url{http://www.avs.com} is a trademark of Advanced
Visualization Systems, and ParaView \url{http://www.paraview.org}
is an open-source visualization platform.
